### 2023-06-27 python_excel_ite.tex
fixed bad quotation marks

\textsf{We have added a basic `simulate` function to our `data_table` and `goal_seek` functions. Python is proving to be quite nice for doing Excel-style "what if?" analysis.}

@@

The first notebook in this submodule starts by explaining what Python packages are and their role in sharing code. We then revisit a concept from earlier in the course - creating a good project folder structure. For this we use what is known as a \code{cookiecutter} that can automatically generate a project folder structure and key files from the answers to a few prompts \cite{cookiecutter}. There are a few different folder layouts used in Python projects and there is a bit of discussion on the folder structure we will use and resources given for exploring this issue further. Students are reminded of the importance of version control and we initialize a git repository for our budding package. The basics of version control were already covered in the first week of the course. My experience is that most students have little exposure to software project management concepts such as project folder structures and version control. This can lead to a jumble of files with incoherent names used as a proxy for version control - \code{whatif\_v1.py}, \code{whatif\_v2.py}, \code{whatif\_final.py}, \code{whatif\_finalfinal.py}, and so on.

>>>>

\textsf{We have added a basic \code{simulate} function to our \code{data\_table} and \code{goal\_seek} functions. Python is proving to be quite nice for doing Excel-style "what if?" analysis.}

@@

The first notebook in this submodule starts by explaining what Python packages are and their role in sharing code. We then revisit a concept from earlier in the course - creating a good project folder structure. For this we use what is known as a \code{cookiecutter} that can automatically generate a project folder structure and key files from the answers to a few prompts \cite{cookiecutter}. There are a few different folder layouts used in Python projects and there is a bit of discussion on the folder structure we will use and resources given for exploring this issue further. Students are reminded of the importance of version control and we initialize a git repository for our budding package. The basics of version control were already covered in the first week of the course. My experience is that most students have little exposure to software project management concepts such as project folder structures and version control. This can lead to a jumble of files with incoherent names used as a proxy for version control -- \code{whatif\_v1.py}, \code{whatif\_v2.py}, \code{whatif\_final.py}, \code{whatif\_finalfinal.py}, and so on.
